Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-05-17 causal-bandit/nips_2016/general.tex
adds ifsup

We now consider the more general problem where the graph structure is known, but arbitrary.

% How do actions map to interventions (we need not only consider singleton interventions).
%

For general graphs, $\P{Y|X_i=j} \neq \P{Y|do(X_i=j)}$ (correlation is not causation). However, if all the variables are observable, any causal distribution $\P{X_1...X_N|do(X_i=j)}$ can be expressed in terms of observational distributions via the truncated factorization formula \cite{Pearl2000}. 
\eq{
\P{X_1...X_N|do(X_i=j)} = 
\prod_{k \neq i}\P{X_k|\parents{X_k}}\delta(X_i - j)\,, 
} 
where $\parents{X_k}$ denotes the parents of $X_k$ and $\delta$ is the dirac delta function.

@@

\eq{
\simpleregret \in \bigo{\sqrt{\frac{m(\eta)}{T} \log\left(2T|\calA|\right)}}\,.
}
\end{theorem}

The proof is in the supplementary materials. Note the regret has the same form as that obtained for Algorithm \ref{alg:simple}, with $m(\eta)$ replacing $m(q)$. Algorithm \ref{alg:simple} assumes only the graph structure and not knowledge of the conditional distributions on $X$. Thus it has broader applicability to the parallel graph than the generic algorithm given here. We believe that Algorithm \ref{alg:general} with the optimal choice of $\eta$ is close to minimax optimal, but leave lower bounds
for future work.

>>>>

We now consider the more general problem where the graph structure is known, but arbitrary. For general graphs, $\P{Y|X_i=j} \neq \P{Y|do(X_i=j)}$ (correlation is not causation). However, if all the variables are observable, any causal distribution $\P{X_1...X_N|do(X_i=j)}$ can be expressed in terms of observational distributions via the truncated factorization formula \cite{Pearl2000}. 
\eq{
\P{X_1...X_N|do(X_i=j)} = 
\prod_{k \neq i}\P{X_k|\parents{X_k}}\delta(X_i - j)\,, 
} 
where $\parents{X_k}$ denotes the parents of $X_k$ and $\delta$ is the dirac delta function.

@@

\eq{
\simpleregret \in \bigo{\sqrt{\frac{m(\eta)}{T} \log\left(2T|\calA|\right)}}\,.
}
\end{theorem}
\ifsup 
The proof is in Section \ref{sec:thm:general}.
\else
The proof is in the supplementary materials.
\fi Note the regret has the same form as that obtained for Algorithm \ref{alg:simple}, with $m(\eta)$ replacing $m(q)$. Algorithm \ref{alg:simple} assumes only the graph structure and not knowledge of the conditional distributions on $X$. Thus it has broader applicability to the parallel graph than the generic algorithm given here. We believe that Algorithm \ref{alg:general} with the optimal choice of $\eta$ is close to minimax optimal, but leave lower bounds
for future work.
